### 2014-06-26 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment Guide: Add some notes to testing procedure
Equipment Guide: Edits to testing procedure

\begin{itemize}
\item Power on the following devices:
    \begin{itemize}
    \item Uninterruptible Power Supplies (UPSs)
    \item WiFi routers
    \item Hose flow / Arduino laptop with NTP, RabbitMQ, Python receive\_data.py script
    \item DAQs and laptops
    \item Gas analyzers (leave running as long as possible during testing)
    \item Digital video recorder (DVR)
    \item Bullet cameras
    \item Thermal imaging cameras (TICs) (check battery level)
    \item Digital video cassette recorders (DVCRs) (check battery level)
    \item GoPros (check battery level)
    \item Video cameras (check battery level)
    \end{itemize}
\end{itemize}

@@

@@

\begin{itemize}
\item Verify testing procedure with all personnel
\item Safety checks

\item Power on gas analyzer pump

\item Turn on water for heat flux gauges

\item Check Arduino battery level
\item Power on Arduino data loggers

\item Start recording on:
    \begin{itemize}
    \item GoPros
    \item Video cameras
    \item DVCRs (Mobile TIC)
    \end{itemize}

\item Start synced recording on: [MARK DATE/TIME]
    \begin{itemize}
    \item DVR
    \item DAQ data
    \end{itemize}

@@

\item Begin test [MARK DATE/TIME]

@@

\item End test [MARK DATE/TIME]

\item Stop synced recording on: [MARK DATE/TIME]
    \begin{itemize}
    \item DAQ
    \item DVR
    \end{itemize}

\item Stop recording on:
    \begin{itemize}
    \item GoPros
    \item Video cameras
    \item DVCRs (Mobile TIC)
    \end{itemize}

@@

@@

\begin{itemize}
\item Retrieve data from:
    \begin{itemize}
    \item DAQ
    \item DVR
    \item GoPros
    \item Video cameras with digital media
    \item Arduinos
    \end{itemize}

\item Swap and label tapes from video cameras and DVCRs as needed

\item Make 3 copies of all data on external hard drives

@@

\item On return from trip, extract video from DVCRs
\end{itemize}

@@

\begin{itemize}
\item Charge all batteries on:
    \begin{itemize}
    \item Laptops
    \item Arduinos
    \item Bullet camera batteries
    \item TICs
    \item GoPros
    \item Video cameras
    \item DVCRs
    \item Radios
    \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
\item Power on the following devices:
    \begin{itemize}
    \item Generators (check oil and gas levels)
    \item Uninterruptible Power Supplies (UPSs)
    \item WiFi routers/repeaters
    \item Arduino laptop with NTP, RabbitMQ, Python receive\_data.py script
    \item DAQs and laptops
    \item Weather stations
    \item Gas analyzers (leave running as long as possible during testing)
    \item Digital video recorder (DVR)
    \item Bullet cameras and power supplies
    \item Thermal imaging cameras (TICs)
    \item Digital video cassette recorders (DVCRs)
    \item GoPros
    \item Video cameras
    \end{itemize}
\end{itemize}

@@

\item Check and record lag time on gas analyzer probes

@@

\begin{itemize}
\item Take GigaPan pictures as needed
\item Distribute still cameras

\item Verify testing procedure with all personnel
\item Safety checks

\item Power on gas analyzer pump
\item Add dry ice to gas sample traps (or turn on gas dryer)

\item Turn on water for heat flux gauges, cool cans, etc.

\item Power on Arduino data loggers

\item Start recording on:
    \begin{itemize}
    \item GoPros (Sync GoPro time to DVR screen time)
    \item Video cameras
    \item Mobile TIC
    \item DAQ
    \item DVR
    \end{itemize}

@@

\item Begin test

@@

\item End test

\item Stop recording on:
    \begin{itemize}
    \item DAQ
    \item DVR
    \item GoPros
    \item Video cameras
    \item Mobile TIC
    \end{itemize}

@@

\item Take GigaPan pictures as needed

@@

\begin{itemize}
\item Collect and organize data from:
    \begin{itemize}
    \item DAQ
    \item DVR
    \item GoPros
    \item GigaPan
    \item Weather station data logger
    \item Mobile TIC
    \item Arduinos
    \item Video cameras with digital media
    \item Still cameras with digital media
    \end{itemize}

\item Archive, swap and label tapes from video cameras and DVCRs if needed

\item Make copies of all data on external hard drives

@@

\item Format GoPros, video and still camera media, mobile TIC, Arduinos, and GigaPan camera

\item On return from trip, extract video from DVCR tapes
\end{itemize}

@@

\begin{itemize}
\item Charge all batteries on:
    \begin{itemize}
    \item Laptops and tablets
    \item 12 V batteries
    \item TICs
    \item GoPros
    \item Video cameras
    \item Still cameras
    \item GigaPan camera
    \item DVCRs
    \item Radios
    \item Arduinos
    \end{itemize}
\end{itemize}
